---
title: "Pipeline Report"
author: "AI-CARE Working Group"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Statistics on Output Data
### Table: Number of Cases by Module and Entity

```{r load_data, echo=FALSE, warnings = FALSE, message = FALSE}
OUTPUT_DIRECTORY <- "Ausgabedaten"

file_name_translation <- c(
  "patient" = "Patient",
  "tumor" = "Tumor",
  "fe" = "Follow-Up Event",
  "modul_mamma" = "Mamma-Ca Module",
  "op" = "Surgery",
  "strahlentherapie" = "Radiation Therapy",
  "systemtherapie" = "Medicinal Therapy"
)
read_outputs <- function(file_name, subfolder=FALSE) {
  if (subfolder==FALSE) {
    path <- paste0(OUTPUT_DIRECTORY, "/gesamt/", file_name, ".csv")
    entity <- "total"
  } else {
    path <- paste0(OUTPUT_DIRECTORY, "/gesamt/", subfolder, "/", subfolder, "_", file_name, ".csv")
    entity <- subfolder
  }
  dta <- read.csv(path)
  N <- nrow(dta)
  if (N==1) {
    if(colnames(dta)[1]=="V1") {
      N <- 0
    }
  }
  return(data.frame(Module = file_name_translation[[file_name]], Entity = entity, N = N))
}
modul_names <- c("patient", "tumor", "modul_mamma", "op", "strahlentherapie", "systemtherapie", "fe")
modul_names_en <- c("Patient","Tumor","Mamma-Ca Module","Surgery","Radiation Therapy","Medicinal Therapy", "Follow-Up Event")
#output_file_names <- list.files(paste0(OUTPUT_DIRECTORY, "/gesamt"), pattern = "\\.csv$")
#output_file_input <- substr(output_file_names, 1, nchar(output_file_names)-4)
output_file_input <- modul_names #output_file_input[output_file_input %in% modul_names]

subfolders_found <- list.dirs(paste0(OUTPUT_DIRECTORY, "/gesamt"), recursive = FALSE, full.names = FALSE)
subfolders_input <- subfolders_found[subfolders_found %in% c("C8", "C34", "C50", "C73")]

output_total <- list()
for (i in 1:length(as.list(c(FALSE, subfolders_input)))) {
  subfolder <- as.list(c(FALSE, subfolders_input))[[i]]
  output_total[[i]] <- lapply(output_file_input, read_outputs, subfolder = subfolder)
}
total_frame <- do.call(rbind, lapply(output_total, function(sublist) {do.call(rbind, sublist)}))
total_frame_wide <- reshape(total_frame, idvar = "Module", timevar = "Entity", direction = "wide")
colnames(total_frame_wide)[colnames(total_frame_wide) == "N.total"] <- "Total"
colnames(total_frame_wide)[colnames(total_frame_wide) == "N.C34"] <- "Lung Cancer"
colnames(total_frame_wide)[colnames(total_frame_wide) == "N.C50"] <- "Breast Cancer"
colnames(total_frame_wide)[colnames(total_frame_wide) == "N.C73"] <- "Thyroid Cancer"
colnames(total_frame_wide)[colnames(total_frame_wide) == "N.C8"] <- "Non-Hodgkin Lymphoma"

knitr::kable(total_frame_wide)
```

### Plot: Number of Cases by Module and Entity

```{r, echo=FALSE, fig.width=10, fig.height=6, warnings = FALSE, message = FALSE}
suppressWarnings(library(ggplot2))
total_frame$Entity[total_frame$Entity == "C34"] <- "Lung Cancer"
total_frame$Entity[total_frame$Entity == "C50"] <- "Breast Cancer"
total_frame$Entity[total_frame$Entity == "C73"] <- "Thyroid Cancer"
total_frame$Entity[total_frame$Entity == "C8"] <- "Non-Hodgkin Lymphoma"
total_frame$Entity[total_frame$Entity == "total"] <- "Total"

ggplot(total_frame, aes(x = factor(Module, level = modul_names_en, ordered=TRUE), y = N, fill = Module)) +
    geom_bar(stat = "identity") +
    geom_text(aes(label = N), y = median(total_frame$N), vjust = 1, size = 3, angle = 90) +
    facet_wrap(~Entity)+
    labs(title = "Number of Cases by Module and Entity",
         x = "Module Name", y = "Count") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    scale_fill_discrete(breaks = modul_names_en)
```

```{r, echo=FALSE}
### Count by Cancer Registry
all_folders <- list.dirs(OUTPUT_DIRECTORY, recursive = FALSE, full.names = FALSE)
register_folder <- all_folders[grep("aicare-", all_folders)]

read_outputs_register <- function(folder_name) {
  all_files <- list.files(paste0(OUTPUT_DIRECTORY, "/", folder_name), pattern = "\\.csv$")
  #modul_files <- all_files[all_files %in% paste0(modul_names, ".csv")]
  #modul_names <- substr(modul_files, 1, nchar(modul_files)-4)
  Ns <- c()
  for (i in 1:length(modul_names)) {
    dta <- read.csv(paste0(OUTPUT_DIRECTORY,"/", folder_name, "/", modul_names[i], ".csv"))
    Nrows <- nrow(dta)
    if (Nrows==1) {
      if(colnames(dta)[1]=="V1") {
        Nrows <- 0
      }
    }
    Ns[i] <- Nrows
  }
  return(data.frame(Registry = folder_name,
                    Module = unname(file_name_translation[modul_names]),
                    N = Ns))
}
register_frame <- do.call("rbind", lapply(register_folder, read_outputs_register))
```

```{r echo=FALSE}
if (!dir.exists(paste0(OUTPUT_DIRECTORY,"/Statistiken"))) {
  dir.create(paste0(OUTPUT_DIRECTORY,"/Statistiken"))
}
write.csv(total_frame, paste0(OUTPUT_DIRECTORY, "/Statistiken", "/", "Cases_by_Entity.csv"))
write.csv(register_frame, paste0(OUTPUT_DIRECTORY, "/Statistiken", "/", "Cases_by_Registry.csv"))
```

### Plot: Number of Cases by Module and Registry

```{r, echo=FALSE, fig.width=10, fig.height=10}
ggplot(register_frame, aes(x = factor(Module, level = modul_names_en), y = N, fill = Module)) +
       geom_bar(stat = "identity") +
       geom_text(aes(label = N), y = median(register_frame$N), vjust = 1, size = 3, angle = 90) +
       facet_wrap(~Registry)+
       labs(title = "Number of Cases by Module and Registry", x = "Module Name", y = "Count") +
       theme_minimal() +
       theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
       scale_fill_discrete(breaks = modul_names_en)

```

## Statistics on Transformations and Removals

### Table: General Frequencies

In this table, the column "Total_Cases" refers to the total number of entries found in the log file. This number results from all removals (column "Total_Removals") as well as all transformations (column "Total_Removals"). Since the same values are often removed or transformed multiple times, the table additionally shows the number of unique frequencies.

\tiny
```{r, echo=FALSE}

halde <- read.csv(paste0(OUTPUT_DIRECTORY, "/halde.csv"))
if (nrow(halde)>2){
  halde_register <- halde[-1, c("register", "table", "variable", "auspraegung", "status")]
  halde_register <- halde_register[!duplicated(halde_register), ]

  N_all <- nrow(halde)-1
  halde <- halde[-1, c("register", "table", "variable", "auspraegung", "status")]
  N_all_deleted <- nrow(subset(halde, status=="deleted"))
  N_all_mapped <- nrow(subset(halde, status=="mapped"))

  halde$register <- "all"
  halde <- halde[!duplicated(halde), ]

  halde$auspraegung[is.na(halde$auspraegung)] <- "NA"
  halde_register$auspraegung[is.na(halde_register$auspraegung)] <- "NA"

  summary_table_halde <- aggregate(register ~ auspraegung + status + variable, data = halde, FUN = length)
  colnames(summary_table_halde)[colnames(summary_table_halde) == "register"] <- "count"

  summary_table_var_total <- aggregate(register ~ status + variable, data = halde, FUN = length)
  colnames(summary_table_var_total)[colnames(summary_table_var_total) == "register"] <- "count"

  halde_unique <- halde[,c("variable", "auspraegung", "status")]
  halde_unique <- halde_unique[!duplicated(halde_unique), ] #no duplicate rows
  N_unique <- nrow(halde_unique)
  N_unique_deleted <- nrow(subset(halde_unique, status=="deleted"))
  N_unique_mapped <- nrow(subset(halde_unique, status=="mapped"))

  summary_general <- data.frame(Total_Cases = N_all,
                          Total_Removals = N_all_deleted,
                          Total_Transformations = N_all_mapped,
                          Unique_Cases = N_unique,
                          Unique_Removals = N_unique_deleted,
                          Unique_Transformations = N_unique_mapped)

  knitr::kable(summary_general) 
} else{
  print("Empty Log File!")
}
```
\normalsize

```{r, echo=FALSE}
if (nrow(halde)>2){
  # by Registry
  register_list_var <- list()
  register_list <- list()
  for (i in 1:length(register_folder)) {
    the_registry <- register_folder[i]
    summary_table_var <- aggregate(register ~ status + variable, data = subset(halde_register, register==the_registry), FUN = length)
    colnames(summary_table_var)[colnames(summary_table_var) == "register"] <- "count"
    summary_table_var$register <- the_registry
    register_list_var[[i]] <- summary_table_var
    summary_table <- aggregate(register ~ auspraegung + status + variable, data = subset(halde_register, register==the_registry),
                              FUN = length)
    colnames(summary_table)[colnames(summary_table) == "register"] <- "count"
    summary_table$register <- the_registry
    register_list[[i]] <- summary_table
  }
  register_halde <- do.call("rbind", register_list)
  register_halde_var <- do.call("rbind", register_list_var)

  write.csv(summary_general, paste0(OUTPUT_DIRECTORY,"/Statistiken", "/", "Cases_by_Entity.csv"))
  write.csv(register_halde_var, paste0(OUTPUT_DIRECTORY,"/Statistiken", "/",  "Halde_Case_Count_Variables_by_Registry.csv"))
  write.csv(register_halde, paste0(OUTPUT_DIRECTORY, "/Statistiken", "/", "Halde_Case_Count_Detail_by_Registry.csv"))
  write.csv(summary_table_var_total,paste0(OUTPUT_DIRECTORY, "/Statistiken", "/", "Halde_Case_Count_Variables.csv"))
  write.csv(summary_table_halde, paste0(OUTPUT_DIRECTORY, "/Statistiken", "/",  "Halde_Case_Count_Detail.csv"))
}
```

### Plot: Number of Unique Removed and Transformed Values by Variable

```{r, echo=FALSE, fig.width=10, fig.height=14}
if (nrow(halde)>2){
  ggplot(summary_table_var_total,
        aes(x = variable, y = count, fill = status)) +
        geom_bar(stat = "identity", position = "dodge") +
        coord_flip()+
        theme_minimal()+
        labs(x = "Variable", y="Count", fill = "Status", title = "Number of Non-conforming Values")+
        theme(axis.text.x=element_text(angle = 45, hjust=1))
}
```
